Wind Veer and Speed in Turbulent Ekman Flow - Part 1: Scaling analysis and universal profile model

### 2024-10-01 write1/manuscript.tex
update

\subsection{Comparison with other theories}

An alternative approach that considers viscous effects close to the surface is the van-Driest scaling \citep{vandriest:JOT1956}, 
where an exponential damping of Prandtl's mixing length is considered near the wall to yield 
\begin{align}
  \frac{\p u^+}{\p y^+} = \frac{2}{ 1+ \sqrt{1+\left(2\kappa y^+\right)^2 (1-\exp\left[-y^+\right])}};
\end{align}
the spanwise component is zero as no rotational effects are considered. 
%
Comparing our proposed formulation (Fig.~\ref{fig:vanDriest}) for the stream-wise velocity in the inner layer to  \citeauthor{vandriest:JOT1956}'s formulation 
yields later convergence of the velocity onto the logarithmic profile while, over all, it serves as an excellent model of the streamwise 
velocity component:
% 
Notable deviations (on the order of few percent) only occur in the region $10 < z^+ < 30$, 
where the velocity transitions from the linear to the logarithmic profile. 
\begin{figure}
  \centerline{\includegraphics[width=0.66\textwidth]{../plot/vanDriest_profile.png}}
  \caption{Near-wall velocity profile according to the 
    van-Driest scaling (blue, solid) in comparison with 
    the present model (red, dashed), 
    the viscous law of the wall (orange dashed), and 
    the logarithmic law (green, solid)} 
  \label{fig:vanDriest}
\end{figure}

For the higher layers of the ABL, the Ekman spiral is the simplest model available. When employed across the entirety of the ABL, the spiral is flattened, corresponding to a reduction of the veering angle both at the surface and throughout the ABL. We, however, find that a modified version of the Ekman spiral explicitly taking into account the surface boundary condition, is a consistent model and yields excellent 
agreement with the velocity profiles from DNS (Sec.~\ref{sec:ekman}).

Given a surface veering, a formulation for the velocity profile in the logartihmic and Ekman layer can be obtained following the arguments by \cite{etling:2008}, cf. \cite{emeis:2018}. This simple model is compared to our DNS data and theoretical profiles in Fig.~\ref{fig:etling}.

>>>>

\subsection{Comparison with other theories}
%%% VAN DRIEST SCALING
An alternative approach that considers viscous effects close to the surface is the van-Driest scaling \citep{vandriest:JOT1956}, 
where an exponential damping of Prandtl's mixing length is considered near the wall to yield 
\begin{align}
  \frac{\p u^+}{\p y^+} = \frac{2}{ 1+ \sqrt{1+\left(2\kappa y^+\right)^2 (1-\exp\left[-y^+\right])}};
\end{align}
the spanwise component is zero as no rotational effects are considered. 
%
Comparing our proposed formulation (Fig.~\ref{fig:vanDriest}) for the stream-wise velocity in the inner layer to  \citeauthor{vandriest:JOT1956}'s formulation 
yields later convergence of the velocity onto the logarithmic profile while, over all, it serves as an excellent model of the streamwise 
velocity component:
% 
Notable deviations (on the order of few percent) only occur in the region $10 < z^+ < 30$, 
where the velocity transitions from the linear to the logarithmic profile. 
\begin{figure}
  \centerline{\includegraphics[width=0.66\textwidth]{../plot/vanDriest_profile.png}}
  \caption{Near-wall velocity profile according to the 
    van-Driest scaling (blue, solid) in comparison with 
    the present model (red, dashed), 
    the viscous law of the wall (orange dashed), and 
    the logarithmic law (green, solid)} 
  \label{fig:vanDriest}
\end{figure}

%EKMAN SPIRAL 
For the higher layers of the ABL, the Ekman spiral is the simplest model available. When employed across the entirety of the ABL, the spiral of a turbulent Ekman layer is flattened with respect to Ekman's lamniar solution, which  corresponds to a reduction of the veering angle both at the surface and throughout the ABL. We, however, find that a modified version of the Ekman spiral explicitly taking into account the surface boundary condition, is a consistent model and yields excellent agreement with the velocity profiles from DNS (Sec.~\ref{sec:ekman}).

%ETLING MODEL 
Given a surface veering, a formulation for the velocity profile in the logartihmic and Ekman layer can be obtained following the arguments by \cite{etling:2008}, cf. \cite{emeis:2018}. This simple model is compared to our DNS data and theoretical profiles in Fig.~\ref{fig:etling}.
